\documentclass{article}

\usepackage{float}
\restylefloat{table}

\usepackage{booktabs}

\title{Team Contributions: Final\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

This document summarizes the contributions of each team member for the final
demonstration and documentation.  The time period of interest is the time
between Rev 0 and the Final documentation.

\section{Team Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 7\\
Grace McKenna & 4\\
Travis Wing & 6\\
Cameron Dunn & 7\\
Kai Arseneau & 4\\
\bottomrule
\end{tabular}
\end{table}

Note that not all team members were present for all team meetings. This is due to some meetings not requiring all team members to be present as they were sub-team specific meetings.
For example, during front end specific meetings, back end sub-team members were not required to attend. For team meetings that required full group attendance, all team members were present.

\section{Supervisor/Stakeholder Meeting Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Meetings}\\
\midrule
Total & 2 \\
Grace McKenna & 1\\
Travis Wing & 2\\
Cameron Dunn & 2\\
Kai Arseneau & 2\\
\bottomrule
\end{tabular}
\end{table}

Grace McKenna was absent during a supervisor meeting due to the flu, this was communicated with both the supervisor and her team.

\section{Lecture Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Grace McKenna & 0\\
Travis Wing & 0 \\
Cameron Dunn & 0 \\
Kai Arseneau & 0\\
\bottomrule
\end{tabular}
\end{table}

\section{TA Document Discussion Attendance}

\begin{table}[H]
\centering
\begin{tabular}{ll}
\toprule
\textbf{Student} & \textbf{Lectures}\\
\midrule
Total & 1\\
Grace McKenna & 1\\
Travis Wing & 1\\
Cameron Dunn & 1\\
Kai Arseneau & 1\\
\bottomrule
\end{tabular}
\end{table}

\section{Commits}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Commits} & \textbf{Percent}\\
\midrule
Total & 38 & 100\% \\
Grace McKenna & 8 & 21.1\% \\
Travis Wing & 11 & 28.9\% \\
Cameron Dunn & 9 & 23.7\% \\
Kai Arseneau & 10& 26.3\% \\
\bottomrule
\end{tabular}
\end{table}

\section{Issue Tracker}

\begin{table}[H]
\centering
\begin{tabular}{lll}
\toprule
\textbf{Student} & \textbf{Authored (O+C)} & \textbf{Assigned (C only)}\\
\midrule
Grace McKenna & 14 & 0 \\
Travis Wing & 12 & 0 \\
Cameron Dunn & 5 & 2 \\
Kai Arseneau & 12 & 4 \\
\bottomrule
\end{tabular}
\end{table}

The issue tracker is a bit skewed because of how our team manages issues, during group meetings some team members create issues that are to be worked on by multiple teammates.
This lead to not all issues being assigned to a specific team member and not all team members having an equal number of authored issues.
\end{document}